### 2024-03-13 options/symbols_and_cmd.tex
1st section of RL chapter
Edit since UQ_TD_full has been completed
Implementation of FC comments on chapter methodo

%% D
\newabbreviation[group={Acronyms}]{DC}{DC}{direct current}
\newabbreviation[group={Acronyms}]{DHN}{DHN}{district heating network}

@@

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{fuel cell}

@@

%% L
\newabbreviation[group={Acronyms}]{LCA}{LCA}{life cycle assessment}
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{levelised cost of energy}
\newabbreviation[group={Acronyms}]{LFO}{LFO}{light fuel oil}
\newabbreviation[group={Acronyms}]{LOO}{LOO}{leave-one-out}
\newabbreviation[group={Acronyms}]{LPG}{LPG}{liquefied petroleum gas}
\newabbreviation[group={Acronyms}]{LT}{LT}{low-temperature}

@@

%% U
\newabbreviation[group={Acronyms}]{UQ}{UQ}{Uncertainty Quantification}

>>>>

%% D
\newabbreviation[group={Acronyms}]{DC}{DC}{direct current}
\newabbreviation[group={Acronyms}]{DHN}{DHN}{district heating network}
\newabbreviation[group={Acronyms}]{DNN}{DNN}{deep neural network}
\newabbreviation[group={Acronyms}]{DRL}{DRL}{deep reinforcement learning}

@@

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{fuel cell}
\newabbreviation[group={Acronyms}]{FEC}{FEC}{final energy consumed}

@@

%% L
\newabbreviation[group={Acronyms}]{LCA}{LCA}{life cycle assessment}
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{levelised cost of energy}
\newabbreviation[group={Acronyms}]{LFO}{LFO}{light fuel oil}
\newabbreviation[group={Acronyms}]{LOO}{LOO}{leave-one-out}
\newabbreviation[group={Acronyms}]{LP}{LP}{linear programming}
\newabbreviation[group={Acronyms}]{LPG}{LPG}{liquefied petroleum gas}
\newabbreviation[group={Acronyms}]{LT}{LT}{low-temperature}

@@

%% U
\newabbreviation[group={Acronyms}]{UQ}{UQ}{uncertainty quantification}
